Human Factors Influencing Visual Statistical Inference

### 2013-06-06 sociology_paper.tex
time taken model - slightly reformulated

%\documentclass{article}
\documentclass[10pt]{article}
\usepackage{times}
%\usepackage{natbib}
%\usepackage{multicol}
\RequirePackage{natbib}
\usepackage{amsmath, amssymb, fullpage, amsthm, array,,graphicx,asa, url}
%\usepackage[dvips]{graphics}

@@

The learning of each observer over a course of $K$ evaluations may be observed as the improvement of the time taken to evaluate a lineup in the later attempts. Suppose $Z_{ijk}$ denotes the time taken for an observer $i$ to evaluate a  lineup $j$ in his/her $k$th attempt. Let $\mu_{ijk}=  E(Z_{ijk})$ be the average time taken by  observer $i$ to pick the data panel from lineup $j$ in his/her $k$th attempt. We model this in a generalized mixed effects model of the form
\begin{equation} \label{eqn:trend_time}
g_1( \mu_{ijk} )= \mu_1 + \alpha_k + u_i +  a_{i} k + \ell_j,  
\end{equation}
where the link function $g_1(\mu)=1/\mu;  \mu >0$ and $\mu_1$ represents the inverse of overall average time taken to evaluate a lineup.

>>>>

%\documentclass{article}
\documentclass[10pt]{article}
\usepackage{times}
%\usepackage{natbib}
%\usepackage{multicol}
\RequirePackage{natbib}
\usepackage[colorlinks=true, citecolor=blue, linkcolor=blue]{hyperref}
\usepackage{amsmath, amssymb, fullpage, amsthm, array,,graphicx,asa, url}
%\usepackage[dvips]{graphics}

@@

The learning of each observer over a course of $K$ evaluations may be observed as the improvement of the time taken to evaluate a lineup in the later attempts. Suppose $Z_{ijk}$ denotes the time taken for an observer $i$ to evaluate a  lineup $j$ in his/her $k$th attempt. Let $\mu_{ijk}=  E(Z_{ijk})$ be the average time taken by  observer $i$ to pick the data panel from lineup $j$ in his/her $k$th attempt. We model this in a generalized mixed effects model of the form
\hh{
\begin{equation} \label{eqn:trend_time}
g( \mu_{ijk} )= \mu + \alpha_1 + \alpha k + u_i +  a_{i} k + \ell_j,  
\end{equation}
where $g$ is now the inverse link function $g(\mu) = 1/\mu$ for positive values of $\mu$. $\mu$ represents the inverse of the overall average time taken by an observer to evaluate a lineup. $\alpha$ is the average change in time taken for each additional attempt.  $\alpha_1$ is an offset in time taken for the first effect. All other effects are random effects: as before, $u_i$ is a subject-specific intercept representing  individual speed of an observer with $u_i \sim N(0, \sigma_u^2)$. $a_i$ is a subject-specific slope representing the deviation of the speed-up (or -down) by attempt $k$. We assume $a_i \sim N(0, \sigma_a^2)$.
$\ell_j$ is a lineup-specific random effect for the time needed to evaluate a lineup; $\ell_j \sim N(0, \sigma_\ell^2)$.
}
\begin{equation} \label{eqn:trend_time}
g_1( \mu_{ijk} )= \mu_1 + \alpha_k + u_i +  a_{i} k + \ell_j,  
\end{equation}
where the link function $g_1(\mu)=1/\mu;  \mu >0$ and $\mu_1$ represents the inverse of overall average time taken to evaluate a lineup.
